### 2020-02-11 main.tex
init commit

\documentclass[10pt,a4paper,twoside]{article}
\input{spp.dat}

%  Editorial staff will uncomment the next line
% \providecommand{\artnum}[0]{XX-XX}
% \renewcommand{\articlenum}[0]{SPP-\the\year-\artnum-}

\begin{document}

\title{\TitleFont Compressive Sensing: Applications from 1-D to $N$-D}

\author[*\negthickspace]{Kenneth V.~Domingo}
\author[ ]{Maricor N.~Soriano
\lastauthorsep}
\affil[ ]{National Institute of Physics, University of the Philippines, Diliman, Quezon City, Philippines}
\affil[*]{\corremail{kdomingo@nip.upd.edu.ph} }

\begin{abstract}
\noindent
Modern signal acquisition technologies are made possible by the Nyquist-Shannon sampling theorem (NST). However, this paradigm is extremely wasteful as the signal is compressed before storing it by systematically discarding the imperceptible information. Compressive sensing (CS) aims to directly sense the information that would otherwise survive this compression stage. Current literature focus exclusively on either audio or image signals, as well as quantifying their reconstruction quality with ambiguous metrics. In this paper, we compressively sample signals of arbitrary dimensions such as those consisting of combinations of audio and images, as well as quantify the reconstruction quality using metrics that are perceptually intuitive.

\keywords{compressive sensing, sub-Nyquist sampling, signal processing}

\end{abstract}

\maketitle
\thispagestyle{titlestyle}

\section{Introduction}\label{sec:intro}

\begin{figure}[tb]
\centering
\includegraphics[width=0.3\linewidth]{figure1.pdf}
\caption{This is an example of a single column-wide figure. Figure captions are preferably self-contained and in vector format (versus raster format).}
\label{fig:plot1}
\end{figure}

\begin{figure}[tbp]
  \centering
  \subfloat[Optional subcaption of this subfigure.]{\makebox[0.4\textwidth]{{\includegraphics[width=0.2\textwidth]{figure1.pdf}\label{fig:f1}}}}
  \quad % or other spacing between figures
  \subfloat{\makebox[0.4\textwidth]{\includegraphics[width=0.3\textwidth]{figure2.jpg}\label{fig:f2}}}
  \caption{Multiple images can be inserted inline.}\label{fig:plots}
\end{figure}

\begin{table}[b]
\centering % center-align tables within a column
\caption{This is an example of a single column table. Captions are preferably self-contained and placed above the table. Columns may be left-, center-, decimal marker-, or right-aligned.}\label{table:label1}
\begin{tabular}{l c d{2.3} r}
\toprule
Example & Count 	1			& \multicolumn{1}{c}{Count 2} & Total\\
\midrule
A 						& 2.345 					& 5.435 																		& 16.78(3)\\
B 						& 3.0 							& 12.0																				& 43.2(5)\\
\bottomrule
\end{tabular}
\end{table}

\section{Methodology}

\section{Results and Discussion}

\section{Conclusions}
Here is the Summary or Conclusions section.

\bibliographystyle{spp-bst}
\bibliography{bibfile}

\end{document}

### 2020-02-11 main.tex
add intro

@@
 \input{spp.dat}
+\usepackage{physics}
+\usepackage{amsfonts}
+\usepackage{graphicx}
+\graphicspath{{images/}}
 
@@
 
-\title{\TitleFont Compressive Sensing: Applications from 1-D to $N$-D}
+\title{\TitleFont Characterization of reconstruction error in compressively sampled speech}
 
@@
 
-\keywords{compressive sensing, sub-Nyquist sampling, signal processing}
+\keywords{compressive sensing, signal processing, compressive speech enhancement}
 
@@
 \section{Introduction}\label{sec:intro}
+Conventional sensing devices are based on the Nyquist-Shannon sampling theorem (NST), which states that given a signal's bandwidth, one can capture all the pertinent information about that signal if it is sampled at a rate
 
-\begin{figure}[tb]
-\centering
-\includegraphics[width=0.3\linewidth]{figure1.pdf}
-\caption{This is an example of a single column-wide figure. Figure captions are preferably self-contained and in vector format (versus raster format).}
-\label{fig:plot1}
-\end{figure}
+\begin{equation} \label{eq:nst}
+	f_S \geq 2f_B
+\end{equation}
 
-\begin{figure}[tbp]
-  \centering
-  \subfloat[Optional subcaption of this subfigure.]{\makebox[0.4\textwidth]{{\includegraphics[width=0.2\textwidth]{figure1.pdf}\label{fig:f1}}}}
-  \quad % or other spacing between figures
-  \subfloat{\makebox[0.4\textwidth]{\includegraphics[width=0.3\textwidth]{figure2.jpg}\label{fig:f2}}}
-  \caption{Multiple images can be inserted inline.}\label{fig:plots}
-\end{figure}
+\noindent where $f_B$ is the signal's highest frequency component, and $2f_B$ is known as the Nyquist rate \cite{Shannon1949}.
+After this sampling process, the information is compressed by exploiting the signal's natural compressibility in some domain.
+For regular consumer-grade and even commercial-grade applications, this tried-and-true method of sampling and systematically discarding the imperceptible information works flawlessly.
+However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful \cite{Candes2008b}.
+Cand\'{e}s et al.
+\cite{Candes2006} and Donoho et al.
+\cite{Donoho2006} independently pioneered compressive sensing (CS), which could directly sample the portions of a signal that would otherwise survive the compression stage in conventional sampling.
+In this new sampling paradigm, we consider the linear model of signal acquisition
 
-\begin{table}[b]
-\centering % center-align tables within a column
-\caption{This is an example of a single column table.
-Captions are preferably self-contained and placed above the table.
-Columns may be left-, center-, decimal marker-, or right-aligned.}\label{table:label1}
-\begin{tabular}{l c d{2.3} r}
-\toprule
-Example & Count 	1			& \multicolumn{1}{c}{Count 2} & Total\\
-\midrule
-A 						& 2.345 					& 5.435 																		& 16.78(3)\\
-B 						& 3.0 							& 12.0																				& 43.2(5)\\
-\bottomrule
-\end{tabular}
-\end{table}
+\begin{equation}\label{eq:cesa}
+	\vec{y} = \vec{A}\vec{x} \equiv \innerproduct{\vec{x}}{\vec{a}_k}
+\end{equation}
+
+In other words, the signal vector $\vec{x} \in \mathbb{R}^n$ is correlated with the basis waveforms $\vec{a}_k$ to yield a compressed information vector $\vec{y} \in \mathbb{R}^m$, where $m \ll n$.
+This causes the task of recovering $\vec{x}$ from $\vec{y}$ impossible since there exist an infinite number of candidate solutions $\bm\hat{\vec{x}}$ which satisfy \eqref{eq:cesa}.
+This can be circumvented by enforcing constraints based on models of natural signals, as well as those based on optimization techniques.
+In particular, reconstruction can be achieved by enforcing sparsity and incoherence constraints \cite{Candes2008b}.
+From this, the process of reconstruction is then recast into a general minimization problem
+
+\begin{equation}\label{eq:minl1}
+	\min_{\vec{x}} \norm{\vec{x}}_1 \quad \textrm{subject to} \quad \vec{A}\vec{x} = \vec{y}
+\end{equation}
+
+\noindent where $\norm{\vec{x}}_1$ denotes the $\ell_1$ norm of $\vec{x}$.
 
@@
 \section{Results and Discussion}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=\textwidth]{clean-pesq-snr.png}
+	\caption{Two most commonly used metrics in evaluating quality of reconstructed speech recordings.
+PESQ is sensitive to the signal compression (left), while the average segmental SNR is sensitive to the number of subbands (right).}
+	\label{fig:pesq-snr}
+\end{figure}
 

### 2020-02-15 main.tex
add metho and R&D

@@
 \graphicspath{{images/}}
+\newcommand{\snrseg}{SNR$_{\mathrm{seg}}$}
 
@@
 
-\title{\TitleFont Characterization of reconstruction error in compressively sampled speech}
+\title{\TitleFont Compressively sampled speech: How good is the recovery?}
 
@@
 However, this paradigm is extremely wasteful as the signal is compressed before storing it by systematically discarding the imperceptible information.
-Compressive sensing (CS) aims to directly sense the information that would otherwise survive this compression stage.
-Current literature focus exclusively on either audio or image signals, as well as quantifying their reconstruction quality with ambiguous metrics.
-In this paper, we compressively sample signals of arbitrary dimensions such as those consisting of combinations of audio and images, as well as quantify the reconstruction quality using metrics that are perceptually intuitive.
+Compressive sensing (CS) aims to directly sense the relevant information.
+Current literature focus either on formulating more computationally-efficient algorithms, or methods which improve the reconstruction quality.
+In this paper, we quantify the reconstruction quality of compressively sampled speech with a perceptually intuitive metric---the Perceptual Evaluation of Speech Quality (PESQ)---and with the standard-use average segmental SNR (\snrseg).
+It is shown that PESQ is sensitive to the compression ratio, while \snrseg~is sensitive to the number of spectrogram subbands.
 
-\keywords{compressive sensing, signal processing, compressive speech enhancement}
+\keywords{compressive sensing, signal processing, spectrogram}
 
@@
 
-\noindent where $f_B$ is the signal's highest frequency component, and $2f_B$ is known as the Nyquist rate \cite{Shannon1949}.
-After this sampling process, the information is compressed by exploiting the signal's natural compressibility in some domain.
-For regular consumer-grade and even commercial-grade applications, this tried-and-true method of sampling and systematically discarding the imperceptible information works flawlessly.
+\noindent where $f_B$ is the signal's highest frequency component, and $2f_B$ is known as the Nyquist rate.
+After this sampling process, the information is compressed by exploiting the signal's natural compressibility in some transform domain.
+For standard consumer-grade and even commercial-grade applications, this tried-and-true method of sampling and systematically discarding the imperceptible information works without a hitch.
 However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful \cite{Candes2008b}.
@@
 \begin{equation}\label{eq:cesa}
-	\vec{y} = \vec{A}\vec{x} \equiv \innerproduct{\vec{x}}{\vec{a}_k}
+	y_k = \vec{x} \cdot \vec{a}_k
 \end{equation}
@@
 
-\noindent where $\norm{\vec{x}}_1$ denotes the $\ell_1$ norm of $\vec{x}$.
+\noindent where $\norm{\vec{x}}_1$ denotes the $\ell_1$ norm of $\vec{x}$. This problem can be solved in a number of ways with various algorithms.
 
-\section{Methodology}
+Romero et al.
+\cite{Romero2016,Romero2018} performed compressive sensing of images in the Fourier domain and showed that it could be used to increase the signal-to-noise ratio of a signal.
+They also showed that such a sampling method was robust against noise.
+In the realm of audio signals, \cite{Mathew2016} constructed sensing matrices using a Gaussian-Logistic map; this was one of the first studies which use chaotic maps instead of random sequences, and is a prelude to the use of CS as an encryption algorithm.
+Through evolutionary algorithms such as differential evolutions, direct reconstruction of CS signals could also be attained in the temporal domain \cite{Andras2018}.
+With audio recordings containing speech, however, the process is not as straightforward.
+Such signals typically use sampling rates of $\sim 10^{3}$ Hz, so it is necessary to process them in slices, in the same way that large images can be processed in patches.
+Low et al.
+\cite{Low2013,Low2018} performed this process by representing a signal in the spectrogram/modulation domain and applying the desired CS algorithm per sampling window.
+
+In this paper, we perform compressive sensing of audio signals containing speech, and quantify the reconstruction quality using the International Telecommunication Standardization Sector (ITU-T) recommendation P.862, otherwise known as the Perceptual Evaluation of Speech Quality (PESQ).
+This metric is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).
+Additionally, the average segmental signal-to-noise ratio (\snrseg), which is commonly used in evaluating audio reconstruction quality, was also used.
+However, unlike the former, this is non-intuitive since its values are unbounded and, for a constant signal, varies with the number of sampling windows.
+We adopt the processing workflow of Low et al.
+while varying the length and number of sampling windows, as well as the compression ratio.
+In contrast with Mathew et al., we stick with the usual sensing matrices derived from i.i.d.
+uniform random samples.
+In an earlier work \cite{Domingo2019}, we compared common algorithms in terms of computation time and reconstruction quality, and showed that LASSO strikes a balance between these two.
+We use this algorithm in this paper to perform the CS reconstruction.
+
+\section{Methodology}\label{sec:metho}
+
+\subsection{Obtaining \& preprocessing the test signals}\label{ssec:timit}
+The test signals used in this paper were obtained from the TIMIT Acoustic-Phonetic Continuous Speech Corpus \cite{timit}, which contains speech recordings, in WAV format, of English speakers separated by region, sex, and spoken sentence.
+All recordings have a sampling rate of 16 kHz and are, on average, 3 seconds long.
+This was then downsampled to 8 kHz to reduce the number of sampling windows needed, and also because the PESQ algorithm only applies to 8 kHz signals.
+
+\subsection{Transforming to a sparse domain}\label{ssec:sparse}
+The first requirement for CS is that a signal should be transformed to some domain where it can be represented sparsely.
+In the case of recorded speech, the most appropriate domain would be the modulation domain, otherwise known as its spectrogram.
+First, we define the length of the sampling window and the percent overlap between adjacent windows, and divide the signal into frames using this sliding window.
+We then multiply each frame by a window function, typically a Hann window defined as
+
+\begin{equation}\label{eq:hann}
+	w[n] = \sin[2](\frac{\pi n}{N}), \quad 0 \leq n \leq N
+\end{equation}
+
+\noindent where $N+1$ is the length of the window. Finally, we take the Fourier transform of each frame. The entire process is also called a short-time Fourier transform and can be summarized as
+
+\begin{equation}\label{eq:stft}
+	X(\omega, p) = \sum_{p=0}^{P-1} x[p] w[p - kR] e^{-i\omega p}
+\end{equation}
+
+\noindent where $x[p]$ indicates the $p$th signal frame, $w[n-k]$ is the window function with hop size $R$, $k$ is the time index, and $\omega$ is the frequency.
+Figure \ref{fig:original} shows a test signal in the temporal domain (top) and its corresponding spectrogram (bottom) with a 25 ms sampling window and 75\% frame overlap.
+
+\subsection{Compressive sensing}\label{ssec:cs}
+The second requirement of CS is that the sensing matrix should be incoherent with the sparse basis.
+Typically, random samples are drawn that are distributed uniformly to simulate compressive measurements.
+We define an index sequence $\xi$ corresponding to a random subset of $m$ samples from the signal.
+The compressed signal vector can be defined as $\vec{y} = \vec{x}_\xi$, and the sensing matrix $\bm\Phi \in \mathbb{R}^{m \times n}$ can be constructed by stacking the columns of a discrete cosine transform (DCT) matrix indexed by $\xi$.
+This sensing matrix can then be used for all the frames.
+After multiplying the frame with a window function as in Section \ref{ssec:sparse}, instead of directly taking the frame's Fourier transform, we can now perform reconstruction of the signal from the compressive measurements.
+The objective of LASSO \cite{scikit-learn} is
+
+\begin{equation}\label{eq:lasso}
+	\min_{\vec{x}} \frac{1}{2m} \norm{\vec{y} - \bm\Phi \vec{x}}_2^2 + \alpha\norm{\vec{x}}_1
+\end{equation}
+
+\noindent where $m$ is the number of samples, and $\alpha$ is the $\ell_1$ regularization parameter.
+
+\subsection{Reconstruction evaluation}\label{ssec:eval}
+Reconstruction quality was evaluated using PESQ, which performs a series of standardized tests modeled after qualitative metrics.
+This algorithm analyzes and compares the reconstructed signal with the original and returns a value from 1 (bad) to 5 (excellent) \cite{pesq}.
+The \snrseg~was also used, which is defined as \cite{Loizou}
+
+\begin{equation}\label{eq:snrseg}
+	\mathrm{SNR_{seg}} = \frac{10}{B} \sum_{b=0}^{B-1} \log_{10} \frac{\sum_{i=Nb}^{Nb+N-1} x_i^2}{\sum_{i=Nb}^{Nb+N-1} \qty(x_i - \hat{x}_i)^2}
+\end{equation}
+
+\noindent where $N$ is the frame length, $B$ is the number of frames, $x_i$ is the original signal, and $\hat{x}_i$ is the reconstructed signal.
 
 \section{Results and Discussion}
+A test signal was chosen at random from the TIMIT corpus, specifically the \texttt{DR8/MJLN0/SA1.wav} file.
+This indicates that the speaker was from dialect region 8 (nomadic), was male with speaker code \texttt{JLN0}, and spoke sentence code \texttt{SA1}, which reads ``She had your dark suit in greasy wash water all year''.
+After downsampling, the signal was compressively sampled with a compression ratio of 40\% using 1024 frames and 75\% frame overlap.
+The optimal regularization $\alpha$ was determined automatically via cross validation, and the reconstruction result is shown in Fig.
+\ref{fig:recovered}.
+Qualitative comparison in the temporal domain shows that the waveforms of the original and reconstructed are similar; in the modulation domain, the dynamic range appears to have decreased, but the dominant frequencies can still be observed.
+Evaluating the PESQ and \snrseg~yields values of 2.50 and 0.07, respectively.
+At face value, we can immediately tell from the PESQ that the reconstructed signal quality is slightly below average.
+However, this distinction cannot be made for the \snrseg~since its bounds are not clearly defined.
+
+Next, the error maps for the signal were generated by compressively sensing the signal and evaluating the metrics for varying compression ratios and number of frames, while keeping the frame overlap constant.
+Figure \ref{fig:pesq-snr} shows the PESQ map (left) and the \snrseg~map (right).
+The former appears to be more sensitive to the signal compression and achieves a value of 4.0 (good) at around 70\% compression.
+The latter tells a different story: it is more sensitive to the number of frames/subbands (as it is an \textit{average} metric) with some additional degradation at lower compression ratios, and achieves a maximum value of around 0.08 at around 1024 frames.
+
+\begin{figure}[tbp]
+	\centering
+	\subfloat[Original]{\makebox[0.46\textwidth]{{\includegraphics[width=0.46\textwidth]{original.png}\label{fig:original}}}}
+	\quad % or other spacing between figures
+	\subfloat[Recovered]{\makebox[0.46\textwidth]{\includegraphics[width=0.46\textwidth]{recovered.png}\label{fig:recovered}}}
+	\caption{Test speech signal obtained from the TIMIT speech corpus with the (a) original signal, and (b) reconstructed signal from compressive measurements.
+The top row is the representation in the time domain, while the bottom row is the spectrogram representation (25 ms sampling window with 75\% overlap).
+The signal reads ``She had your dark suit in greasy wash water all year''.}\label{fig:spectrogram}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{clean-pesq-snr.png}
+	\includegraphics[width=\textwidth]{metrics.png}
 	\caption{Two most commonly used metrics in evaluating quality of reconstructed speech recordings.
-PESQ is sensitive to the signal compression (left), while the average segmental SNR is sensitive to the number of subbands (right).}
+PESQ is sensitive to the signal compression (left), while the \snrseg~is sensitive to the number of subbands (right).}
 	\label{fig:pesq-snr}

### 2020-02-24 main.tex
completed first draft

@@
 Current literature focus either on formulating more computationally-efficient algorithms, or methods which improve the reconstruction quality.
-In this paper, we quantify the reconstruction quality of compressively sampled speech with a perceptually intuitive metric---the Perceptual Evaluation of Speech Quality (PESQ)---and with the standard-use average segmental SNR (\snrseg).
-It is shown that PESQ is sensitive to the compression ratio, while \snrseg~is sensitive to the number of spectrogram subbands.
+In this paper, we quantify the reconstruction quality of compressively sampled speech with a perceptually intuitive metric---the Perceptual Evaluation of Speech Quality (PESQ)---and with the standard average segmental SNR (\snrseg).
+It is shown that the quality of recovery of compressively sampled speech depends on the compression ratio and number of subbands used to represent the signal in the spectrogram domain.
 
@@
 For standard consumer-grade and even commercial-grade applications, this tried-and-true method of sampling and systematically discarding the imperceptible information works without a hitch.
-However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful \cite{Candes2008b}.
+However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful.
 Cand\'{e}s et al.
@@
 Low et al.
-\cite{Low2013,Low2018} performed this process by representing a signal in the spectrogram/modulation domain and applying the desired CS algorithm per sampling window.
+\cite{Low2018} performed this process by representing a signal in the spectrogram/modulation domain and applying the desired CS algorithm per sampling window.
 
@@
 while varying the length and number of sampling windows, as well as the compression ratio.
-In contrast with Mathew et al., we stick with the usual sensing matrices derived from i.i.d.
-uniform random samples.
+In contrast with Mathew et al., we stick with the usual sensing matrices derived from i.i.d.~uniform random samples.
 In an earlier work \cite{Domingo2019}, we compared common algorithms in terms of computation time and reconstruction quality, and showed that LASSO strikes a balance between these two.
@@
 First, we define the length of the sampling window and the percent overlap between adjacent windows, and divide the signal into frames using this sliding window.
-We then multiply each frame by a window function, typically a Hann window defined as
+We then multiply each frame by a window function, typically a Hann window, defined as
 
@@
 After downsampling, the signal was compressively sampled with a compression ratio of 40\% using 1024 frames and 75\% frame overlap.
-The optimal regularization $\alpha$ was determined automatically via cross validation, and the reconstruction result is shown in Fig.
+The optimal regularization $\alpha$ was determined automatically via 5-fold cross validation, and the reconstruction result is shown in Fig.
 \ref{fig:recovered}.
@@
 
-Next, the error maps for the signal were generated by compressively sensing the signal and evaluating the metrics for varying compression ratios and number of frames, while keeping the frame overlap constant.
+Next, the error maps for the signal were generated by compressively sensing the signal and evaluating the metrics for varying compression ratios $m/n \in [0.1, 0.9]$ (in increments of 0.1) and number of frames/subbands $\in \qty{128, 256, 512, 1024}$, while keeping the frame overlap constant.
 Figure \ref{fig:pesq-snr} shows the PESQ map (left) and the \snrseg~map (right).
-The former appears to be more sensitive to the signal compression and achieves a value of 4.0 (good) at around 70\% compression.
-The latter tells a different story: it is more sensitive to the number of frames/subbands (as it is an \textit{average} metric) with some additional degradation at lower compression ratios, and achieves a maximum value of around 0.08 at around 1024 frames.
+The former exhibits sensitivity to the compression ratio and achieves a value of 4.0 (good) at around 70\% compression.
+The latter tells a different story: it shows sensitivity towards the number of frames/subbands (as it is an \textit{average} metric) with some additional degradation at lower compression ratios, and achieves a maximum value of 0.08 at around 1024 frames.
 
@@
 \section{Conclusions}
-Here is the Summary or Conclusions section.
+The reconstruction quality of compressively sampled audio signals containing speech recordings was shown to be dependent on two distinct factors, as well as the metric being used.
+Evaluation of a perceptually intuitive metric such as PESQ shows that it is sensitive to changes in compression, wherein a compression ratio of 60\% is sufficient to yield an average (3.0) PESQ score.
+On the other hand, evaluation of a statistically-based metric such as \snrseg~shows that it is sensitive to changes in the number of frames used to represent the signal in the spectrogram domain, where the use of more frames yields a higher \snrseg~score.
 

### 2020-03-10 listofchanges1.tex
1st rev: add motivation for pesq & snrseg

\section*{List of changes}

\newcommand{\pagelineref}[1]{Page~\pageref{#1}, Line~\lineref{#1}}

\begin{itemize}
	\item \pagelineref{ln:daily-tasks}: Replaced
			\begin{quotation}
				For standard \textbf{consumer-grade and even commercial-grade applications}, this tried-and-true method of sampling and systematically discarding the imperceptible information \textbf{works without a hitch}.
			\end{quotation}
		\noindent with
			\begin{quotation}
				For standard \textbf{daily tasks}, this tried-and-true method of sampling and systematically discarding the imperceptible information \textbf{is acceptable for most applications}.
			\end{quotation}
		\noindent The reason for the first correction is that the recommended correction repeated the word ``application'' from the first.
	\item \pagelineref{ln:from-this}: Split long sentence into two shorter sentences; fixed verb tenses.
	\item \pagelineref{ln:mathew}: Added authors' surnames to inline citation.
	\item \pagelineref{ln:theirs}: Split another long sentence.
	\item \pagelineref{ln:motivation} Moved the first sentence (``This metric is a full reference...'') to Subsec.~\ref{ssec:eval} on \pagelineref{ln:pesq-reference}; added the motivation for using PESQ.
	\item \pagelineref{ln:motivation-snrseg}: Added short description and motivation for \snrseg; added the goal of observing the effect of compression ratio/number of sampling windows vs metrics.
\end{itemize}

### 2020-03-10 main.tex
1st rev: add motivation for pesq & snrseg

@@
 \documentclass[10pt,a4paper,twoside]{article}
-\input{spp.dat}
+\input{spp}
 \usepackage{physics}
 \usepackage{amsfonts}
+\usepackage{changes}
 \usepackage{graphicx}
 \graphicspath{{images/}}
+\usepackage{lineno}
+\renewcommand\linenumberfont{\normalfont\tiny\ttfamily}
+\linenumbers
 \newcommand{\snrseg}{SNR$_{\mathrm{seg}}$}
+
+\makeatletter
+\@namedef{Changes@AuthorColor}{red}
+\colorlet{Changes@Color}{red}
+\makeatother
 
@@
 \begin{document}
+
+\include{listofchanges1}
 
@@
 After this sampling process, the information is compressed by exploiting the signal's natural compressibility in some transform domain.
-For standard consumer-grade and even commercial-grade applications, this tried-and-true method of sampling and systematically discarding the imperceptible information works without a hitch.
+For standard \linelabel{ln:daily-tasks}\replaced{daily tasks}{consumer-grade and even commercial-grade applications}, this tried-and-true method of sampling and systematically discarding the imperceptible information \replaced{is acceptable for most applications}{works without a hitch}.
 However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful.
@@
 In particular, reconstruction can be achieved by enforcing sparsity and incoherence constraints \cite{Candes2008b}.
-From this, the process of reconstruction is then recast into a general minimization problem
+\linelabel{ln:from-this}\deleted{From this,} The process of reconstruction \replaced{can}{is} then \added{be} recast into a general minimization problem
 
@@
 They also showed that such a sampling method was robust against noise.
-In the realm of audio signals, \cite{Mathew2016} constructed sensing matrices using a Gaussian-Logistic map; this was one of the first studies which use chaotic maps instead of random sequences, and is a prelude to the use of CS as an encryption algorithm.
+In the realm of audio signals, \linelabel{ln:mathew}\added{Mathew \& Premanand} \cite{Mathew2016} constructed sensing matrices using a Gaussian-Logistic map\linelabel{ln:theirs}\replaced{.
+Theirs}{; this} was one of the first studies which use chaotic maps instead of random sequences, and is a prelude to the use of CS as an encryption algorithm.
 Through evolutionary algorithms such as differential evolutions, direct reconstruction of CS signals could also be attained in the temporal domain \cite{Andras2018}.
@@
 In this paper, we perform compressive sensing of audio signals containing speech, and quantify the reconstruction quality using the International Telecommunication Standardization Sector (ITU-T) recommendation P.862, otherwise known as the Perceptual Evaluation of Speech Quality (PESQ).
-This metric is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).
-Additionally, the average segmental signal-to-noise ratio (\snrseg), which is commonly used in evaluating audio reconstruction quality, was also used.
-However, unlike the former, this is non-intuitive since its values are unbounded and, for a constant signal, varies with the number of sampling windows.
-We adopt the processing workflow of Low et al.
+\linelabel{ln:motivation}\deleted{This metric is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).} \added{Current metrics for evaluating reconstructed speech quality which are based on the statistical properties of the signal, such as mean-squared error (MSE) and peak signal-to-noise ratio (PSNR), are non-intuitive and have undefined bounds.
+Contrary to this, PESQ is an objective speech quality assessment primarily modeled after an older subjective scoring system, essentially emulating how a group of people may rate a signal from 1 (bad) to 5 (excellent) given a clean reference signal \cite{pesq}.} Additionally, the average segmental signal-to-noise ratio (\snrseg), which is commonly used in evaluating window-sampled audio reconstruction quality, was also used.
+However, \linelabel{ln:motivation-snrseg}\replaced{its values are}{unlike the former, this is } non-intuitive \replaced{since it is also based on the statistical properties of the signal.}{since its values are unbounded and, for a constant signal,} \added{Consequently, its value also varies with the number of sampling windows, which is an important variable to be explored in this paper.
+Furthermore, we are also interested in how changing the compression ratio and/or number of sampling windows affect the reconstruction quality in terms of these two metrics.} We adopt the processing workflow of Low et al.
 while varying the length and number of sampling windows, as well as the compression ratio.
@@
 \subsection{Reconstruction evaluation}\label{ssec:eval}
-Reconstruction quality was evaluated using PESQ, which performs a series of standardized tests modeled after qualitative metrics.
-This algorithm analyzes and compares the reconstructed signal with the original and returns a value from 1 (bad) to 5 (excellent) \cite{pesq}.
-The \snrseg~was also used, which is defined as \cite{Loizou}
+Reconstruction quality was evaluated using PESQ, \linelabel{ln:pesq-reference}\replaced{which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).}{which performs a series of standardized tests modeled after qualitative metrics}.
+\deleted{This algorithm analyzes and compares the reconstructed signal with the original and returns a value from 1 (bad) to 5 (excellent) \cite{pesq}}.
+The \snrseg~was also used, which is defined \cite{Loizou} as
 
@@
 
-\noindent where $N$ is the frame length, $B$ is the number of frames, $x_i$ is the original signal, and $\hat{x}_i$ is the reconstructed signal.
+\noindent where $N$ is the frame length, $B$ is the number of frames, $x_i$ \replaced{are}{is} the original signal \added{samples}, and $\hat{x}_i$ \replaced{are}{is} the reconstructed signal \added{samples}.
 

### 2020-03-12 listofchanges1.tex
2nd rev: rephrase PESQ findings, enlarge figure labels

@@
 \begin{itemize}
-	\item \pagelineref{ln:daily-tasks}: Replaced
-			\begin{quotation}
-				For standard \textbf{consumer-grade and even commercial-grade applications}, this tried-and-true method of sampling and systematically discarding the imperceptible information \textbf{works without a hitch}.
-			\end{quotation}
-		\noindent with
-			\begin{quotation}
-				For standard \textbf{daily tasks}, this tried-and-true method of sampling and systematically discarding the imperceptible information \textbf{is acceptable for most applications}.
-			\end{quotation}
-		\noindent The reason for the first correction is that the recommended correction repeated the word ``application'' from the first.
-	\item \pagelineref{ln:from-this}: Split long sentence into two shorter sentences; fixed verb tenses.
-	\item \pagelineref{ln:mathew}: Added authors' surnames to inline citation.
-	\item \pagelineref{ln:theirs}: Split another long sentence.
-	\item \pagelineref{ln:motivation} Moved the first sentence (``This metric is a full reference...'') to Subsec.~\ref{ssec:eval} on \pagelineref{ln:pesq-reference}; added the motivation for using PESQ.
-	\item \pagelineref{ln:motivation-snrseg}: Added short description and motivation for \snrseg; added the goal of observing the effect of compression ratio/number of sampling windows vs metrics.
+	\item \pagelineref{ln:pesq-abstract}: Restated PESQ findings.
+	\item \pagelineref{ln:pesq-conc}: Edited conclusion to reflect changes in abstract.
+	\item Page~\pageref{fig:pesq-snr}: Made Fig.~2 labels larger.
+	\item Removed some extra information and references so as not to exceed 4 pages (pero mukhang mag-eexceed pa rin po).
+	\item Abbreviated ``compression ratio'' to ``CR''
 \end{itemize}

### 2020-03-12 main.tex
2nd rev: rephrase PESQ findings, enlarge figure labels

--- 2020-02-24 main.tex
@@
 In this paper, we quantify the reconstruction quality of compressively sampled speech with a perceptually intuitive metric---the Perceptual Evaluation of Speech Quality (PESQ)---and with the standard average segmental SNR (\snrseg).
-It is shown that the quality of recovery of compressively sampled speech depends on the compression ratio and number of subbands used to represent the signal in the spectrogram domain.
+It is shown that the quality of recovery of compressively sampled speech \linelabel{ln:pesq-abstract}\added{evaluated using PESQ is dependent on the compression ratio, and independent of the}\deleted{number of spectrogram subbands depends on the compression ratio and} number of subbands used to represent the signal in the spectrogram domain.
 
@@
 After this sampling process, the information is compressed by exploiting the signal's natural compressibility in some transform domain.
-For standard consumer-grade and even commercial-grade applications, this tried-and-true method of sampling and systematically discarding the imperceptible information works without a hitch.
+For standard daily tasks, this tried-and-true method of sampling and systematically discarding the imperceptible information is acceptable for most applications.
 However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful.
@@
 This causes the task of recovering $\vec{x}$ from $\vec{y}$ impossible since there exist an infinite number of candidate solutions $\bm\hat{\vec{x}}$ which satisfy \eqref{eq:cesa}.
-This can be circumvented by enforcing constraints based on models of natural signals, as well as those based on optimization techniques.
-In particular, reconstruction can be achieved by enforcing sparsity and incoherence constraints \cite{Candes2008b}.
-From this, the process of reconstruction is then recast into a general minimization problem
+This can be circumvented by enforcing \added{sparsity and incoherence constraints \cite{Candes2008b}} based on models of natural signals\deleted{, as well as those based on optimization techniques}.
+\deleted{In particular, reconstruction can be achieved by enforcing sparsity and incoherence constraints \cite{Candes2008b}.} The process of reconstruction can then be recast into a general minimization problem
 
@@
 
-\noindent where $\norm{\vec{x}}_1$ denotes the $\ell_1$ norm of $\vec{x}$. This problem can be solved in a number of ways with various algorithms.
+\noindent where $\norm{\vec{x}}_1$ denotes the $\ell_1$ norm of $\vec{x}$. This problem can be solved\deleted{in a number of ways} with various algorithms.
 
 Romero et al.
-\cite{Romero2016,Romero2018} performed compressive sensing of images in the Fourier domain and showed that it could be used to increase the signal-to-noise ratio of a signal.
-They also showed that such a sampling method was robust against noise.
-In the realm of audio signals, \cite{Mathew2016} constructed sensing matrices using a Gaussian-Logistic map; this was one of the first studies which use chaotic maps instead of random sequences, and is a prelude to the use of CS as an encryption algorithm.
-Through evolutionary algorithms such as differential evolutions, direct reconstruction of CS signals could also be attained in the temporal domain \cite{Andras2018}.
+\cite{Romero2016} performed compressive sensing of images in the Fourier domain and showed that it could be used to increase the signal-to-noise ratio of a signal.
+\deleted{They also showed that such a sampling method was robust against noise.} In the realm of audio signals, Mathew \& Premanand \cite{Mathew2016} constructed sensing matrices using a Gaussian-Logistic map.
+Theirs was one of the first studies which use chaotic maps instead of random sequences\deleted{, and is a prelude to the use of CS as an encryption algorithm}.
+Through evolutionary algorithms such as differential evolution, direct reconstruction of CS signals could also be attained in the temporal domain \cite{Andras2018}.
 With audio recordings containing speech, however, the process is not as straightforward.
@@
 
-In this paper, we perform compressive sensing of audio signals containing speech, and quantify the reconstruction quality using the International Telecommunication Standardization Sector (ITU-T) recommendation P.862, otherwise known as the Perceptual Evaluation of Speech Quality (PESQ).
-This metric is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).
-Additionally, the average segmental signal-to-noise ratio (\snrseg), which is commonly used in evaluating audio reconstruction quality, was also used.
-However, unlike the former, this is non-intuitive since its values are unbounded and, for a constant signal, varies with the number of sampling windows.
+In this paper, we perform compressive sensing of audio signals containing speech, and quantify the reconstruction quality using the\deleted{International Telecommunication Standardization Sector (ITU-T) recommendation P.862, otherwise known as the} Perceptual Evaluation of Speech Quality (PESQ).
+Current metrics for evaluating reconstructed speech quality which are based on the statistical properties of the signal, such as mean-squared error (MSE) and peak signal-to-noise ratio (PSNR), are non-intuitive and have undefined bounds.
+The former indicates that it is difficult to gauge and compare the quality of a signal with an MSE value of 0.1, compared to another with an MSE value of 0.01 without explicitly observing them, while the latter yields values that may change depending on the length of the signal or of the sampling window, implying some degree of scale-variance.
+On the other hand, PESQ is an objective speech quality assessment primarily modeled after an older subjective scoring system, essentially emulating how a person might rate a signal from 1 (bad) to 5 (excellent) given a clean reference signal \cite{pesq}.
+Thus, it is easy to gauge a signal's quality based on the PESQ value without actually observing the signal itself.
+Additionally, the average segmental signal-to-noise ratio (\snrseg), which is commonly used in evaluating window-sampled audio reconstruction quality, was also used.
+However, its values are non-intuitive since it is also based on the statistical properties of the signal.
+Consequently, its value also varies with the number of sampling windows, which is an important variable to be explored in this paper.
+Furthermore, we are also interested in how changing the compression ratio \added{(CR)} and/or number of sampling windows affect the reconstruction quality in terms of these two metrics.
 We adopt the processing workflow of Low et al.
-while varying the length and number of sampling windows, as well as the compression ratio.
+while varying the length and number of sampling windows, as well as the \replaced{CR}{compression ratio}.
 In contrast with Mathew et al., we stick with the usual sensing matrices derived from i.i.d.~uniform random samples.
@@
 The test signals used in this paper were obtained from the TIMIT Acoustic-Phonetic Continuous Speech Corpus \cite{timit}, which contains speech recordings, in WAV format, of English speakers separated by region, sex, and spoken sentence.
-All recordings have a sampling rate of 16 kHz and are, on average, 3 seconds long.
+All recordings have a sampling rate of 16 kHz and are\deleted{, on average,} 3 seconds long \added{on average}.
 This was then downsampled to 8 kHz to reduce the number of sampling windows needed, and also because the PESQ algorithm only applies to 8 kHz signals.
@@
 \noindent where $x[p]$ indicates the $p$th signal frame, $w[n-k]$ is the window function with hop size $R$, $k$ is the time index, and $\omega$ is the frequency.
-Figure \ref{fig:original} shows a test signal in the temporal domain (top) and its corresponding spectrogram (bottom) with a 25 ms sampling window and 75\% frame overlap.
+Figure~\ref{fig:original} shows a test signal in the temporal domain (top) and its corresponding spectrogram (bottom) with a 25 ms sampling window and 75\% frame overlap.
 
@@
 This sensing matrix can then be used for all the frames.
-After multiplying the frame with a window function as in Section \ref{ssec:sparse}, instead of directly taking the frame's Fourier transform, we can now perform reconstruction of the signal from the compressive measurements.
+After multiplying the frame with a window function\deleted{as in Section~\ref{ssec:sparse}}, instead of directly taking the frame's Fourier transform, we can now perform reconstruction of the signal from the compressive measurements.
 The objective of LASSO \cite{scikit-learn} is
@@
 \subsection{Reconstruction evaluation}\label{ssec:eval}
-Reconstruction quality was evaluated using PESQ, which performs a series of standardized tests modeled after qualitative metrics.
-This algorithm analyzes and compares the reconstructed signal with the original and returns a value from 1 (bad) to 5 (excellent) \cite{pesq}.
-The \snrseg~was also used, which is defined as \cite{Loizou}
+Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).
+The \snrseg~was also used, which is defined \cite{Loizou} as
 
@@
 
-\noindent where $N$ is the frame length, $B$ is the number of frames, $x_i$ is the original signal, and $\hat{x}_i$ is the reconstructed signal.
+\noindent where $N$ is the frame length, $B$ is the number of frames, $x_i$ are  the original signal samples, and $\hat{x}_i$ are the reconstructed signal samples.
 
@@
 This indicates that the speaker was from dialect region 8 (nomadic), was male with speaker code \texttt{JLN0}, and spoke sentence code \texttt{SA1}, which reads ``She had your dark suit in greasy wash water all year''.
-After downsampling, the signal was compressively sampled with a compression ratio of 40\% using 1024 frames and 75\% frame overlap.
-The optimal regularization $\alpha$ was determined automatically via 5-fold cross validation, and the reconstruction result is shown in Fig.
-\ref{fig:recovered}.
+After downsampling, the signal was compressively sampled with a \replaced{CR}{compression ratio} of 40\% using 1024 frames and 75\% frame overlap.
+The optimal regularization $\alpha$ was determined automatically via 5-fold cross validation, and the reconstruction result is shown in Fig.~\ref{fig:recovered}.
 Qualitative comparison in the temporal domain shows that the waveforms of the original and reconstructed are similar; in the modulation domain, the dynamic range appears to have decreased, but the dominant frequencies can still be observed.
@@
 
-Next, the error maps for the signal were generated by compressively sensing the signal and evaluating the metrics for varying compression ratios $m/n \in [0.1, 0.9]$ (in increments of 0.1) and number of frames/subbands $\in \qty{128, 256, 512, 1024}$, while keeping the frame overlap constant.
+Next, the error maps for the signal were generated by compressively sensing the signal and evaluating the metrics for varying \replaced{CR}{compression ratios} $m/n \in [0.1, 0.9]$ (in increments of 0.1) and number of frames/subbands $\in \qty{128, 256, 512, 1024}$, while keeping the frame overlap constant.
 Figure \ref{fig:pesq-snr} shows the PESQ map (left) and the \snrseg~map (right).
-The former exhibits sensitivity to the compression ratio and achieves a value of 4.0 (good) at around 70\% compression.
-The latter tells a different story: it shows sensitivity towards the number of frames/subbands (as it is an \textit{average} metric) with some additional degradation at lower compression ratios, and achieves a maximum value of 0.08 at around 1024 frames.
+The former exhibits sensitivity to the \replaced{CR}{compression ratio} and achieves a value of 4.0 (good) at around 70\% compression.
+The latter tells a different story: it shows sensitivity towards the number of frames/subbands (as it is an \textit{average} metric) with some additional degradation at lower \replaced{CR}{compression ratios}, and achieves a maximum value of 0.08 at around 1024 frames.
 
@@
 \section{Conclusions}
-The reconstruction quality of compressively sampled audio signals containing speech recordings was shown to be dependent on two distinct factors, as well as the metric being used.
-Evaluation of a perceptually intuitive metric such as PESQ shows that it is sensitive to changes in compression, wherein a compression ratio of 60\% is sufficient to yield an average (3.0) PESQ score.
-On the other hand, evaluation of a statistically-based metric such as \snrseg~shows that it is sensitive to changes in the number of frames used to represent the signal in the spectrogram domain, where the use of more frames yields a higher \snrseg~score.
+The reconstruction quality of compressively sampled audio signals containing speech recordings was \linelabel{ln:pesq-conc}\replaced{described by varying}{shown to be dependent on} two distinct factors\added{, namely, the compression ratio and number of subbands/sampling windows.}\deleted{as well as the metric being used.} Evaluation of a perceptually intuitive metric such as PESQ shows that it is sensitive to changes in compression \added{but independent of the number of spectrogram subbands}, wherein a compression ratio of 60\% is sufficient to yield an average (3.0) PESQ score.
+On the other hand, evaluation of a statistically-based metric such as \snrseg~shows that it is sensitive to changes in the number of \replaced{subbands}{frames} used to represent the signal in the spectrogram domain, where the use of more frames yields a higher \snrseg~score.
 

### 2020-03-14 main.tex
push for submission

@@
 \graphicspath{{images/}}
-\usepackage{lineno}
-\renewcommand\linenumberfont{\normalfont\tiny\ttfamily}
-\linenumbers
 \newcommand{\snrseg}{SNR$_{\mathrm{seg}}$}
 
-\makeatletter
-\@namedef{Changes@AuthorColor}{red}
-\colorlet{Changes@Color}{red}
-\makeatother
+%\makeatletter
+%\@namedef{Changes@AuthorColor}{red}
+%\colorlet{Changes@Color}{red}
+%\makeatother
 
@@
 \begin{document}
-
-\include{listofchanges1}
 
@@
 In this paper, we quantify the reconstruction quality of compressively sampled speech with a perceptually intuitive metric---the Perceptual Evaluation of Speech Quality (PESQ)---and with the standard average segmental SNR (\snrseg).
-It is shown that the quality of recovery of compressively sampled speech \linelabel{ln:pesq-abstract}\added{evaluated using PESQ is dependent on the compression ratio, and independent of the}\deleted{number of spectrogram subbands depends on the compression ratio and} number of subbands used to represent the signal in the spectrogram domain.
+It is shown that the quality of recovery of compressively sampled speech evaluated using PESQ is dependent on the compression ratio, and independent of the number of subbands used to represent the signal in the spectrogram domain.
 
@@
 This causes the task of recovering $\vec{x}$ from $\vec{y}$ impossible since there exist an infinite number of candidate solutions $\bm\hat{\vec{x}}$ which satisfy \eqref{eq:cesa}.
-This can be circumvented by enforcing \added{sparsity and incoherence constraints \cite{Candes2008b}} based on models of natural signals\deleted{, as well as those based on optimization techniques}.
-\deleted{In particular, reconstruction can be achieved by enforcing sparsity and incoherence constraints \cite{Candes2008b}.} The process of reconstruction can then be recast into a general minimization problem
+This can be circumvented by enforcing sparsity and incoherence constraints \cite{Candes2008b} based on models of natural signals.
+The process of reconstruction can then be recast into a general minimization problem
 
@@
 
-\noindent where $\norm{\vec{x}}_1$ denotes the $\ell_1$ norm of $\vec{x}$. This problem can be solved\deleted{in a number of ways} with various algorithms.
+\noindent where $\norm{\vec{x}}_1$ denotes the $\ell_1$ norm of $\vec{x}$. This problem can be solved with various algorithms.
 
@@
 \cite{Romero2016} performed compressive sensing of images in the Fourier domain and showed that it could be used to increase the signal-to-noise ratio of a signal.
-\deleted{They also showed that such a sampling method was robust against noise.} In the realm of audio signals, Mathew \& Premanand \cite{Mathew2016} constructed sensing matrices using a Gaussian-Logistic map.
-Theirs was one of the first studies which use chaotic maps instead of random sequences\deleted{, and is a prelude to the use of CS as an encryption algorithm}.
+In the realm of audio signals, Mathew \& Premanand \cite{Mathew2016} constructed sensing matrices using a Gaussian-Logistic map.
+Theirs was one of the first studies which use chaotic maps instead of random sequences.
 Through evolutionary algorithms such as differential evolution, direct reconstruction of CS signals could also be attained in the temporal domain \cite{Andras2018}.
@@
 
-In this paper, we perform compressive sensing of audio signals containing speech, and quantify the reconstruction quality using the\deleted{International Telecommunication Standardization Sector (ITU-T) recommendation P.862, otherwise known as the} Perceptual Evaluation of Speech Quality (PESQ).
+In this paper, we perform compressive sensing of audio signals containing speech, and quantify the reconstruction quality using the Perceptual Evaluation of Speech Quality (PESQ).
 Current metrics for evaluating reconstructed speech quality which are based on the statistical properties of the signal, such as mean-squared error (MSE) and peak signal-to-noise ratio (PSNR), are non-intuitive and have undefined bounds.
@@
 Consequently, its value also varies with the number of sampling windows, which is an important variable to be explored in this paper.
-Furthermore, we are also interested in how changing the compression ratio \added{(CR)} and/or number of sampling windows affect the reconstruction quality in terms of these two metrics.
+Furthermore, we are also interested in how changing the compression ratio (CR) and/or number of sampling windows affect the reconstruction quality in terms of these two metrics.
 We adopt the processing workflow of Low et al.
-while varying the length and number of sampling windows, as well as the \replaced{CR}{compression ratio}.
+while varying the length and number of sampling windows, as well as the CR.
 In contrast with Mathew et al., we stick with the usual sensing matrices derived from i.i.d.~uniform random samples.
@@
 The test signals used in this paper were obtained from the TIMIT Acoustic-Phonetic Continuous Speech Corpus \cite{timit}, which contains speech recordings, in WAV format, of English speakers separated by region, sex, and spoken sentence.
-All recordings have a sampling rate of 16 kHz and are\deleted{, on average,} 3 seconds long \added{on average}.
+All recordings have a sampling rate of 16 kHz and are 3 seconds long on average.
 This was then downsampled to 8 kHz to reduce the number of sampling windows needed, and also because the PESQ algorithm only applies to 8 kHz signals.
@@
 This sensing matrix can then be used for all the frames.
-After multiplying the frame with a window function\deleted{as in Section~\ref{ssec:sparse}}, instead of directly taking the frame's Fourier transform, we can now perform reconstruction of the signal from the compressive measurements.
-The objective of LASSO \cite{scikit-learn} is
+After multiplying the frame with a window function, instead of directly taking the frame's Fourier transform, we can now perform reconstruction of the signal from the compressive measurements.
+The objective of LASSO is
 
@@
 \subsection{Reconstruction evaluation}\label{ssec:eval}
-Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).
-The \snrseg~was also used, which is defined \cite{Loizou} as
+Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS). The \snrseg~, defined as
 
@@
 
-\noindent where $N$ is the frame length, $B$ is the number of frames, $x_i$ are  the original signal samples, and $\hat{x}_i$ are the reconstructed signal samples.
+\noindent was also used, where $N$ is the frame length, $B$ is the number of frames, $x_i$ are  the original signal samples, and $\hat{x}_i$ are the reconstructed signal samples.
 
@@
 This indicates that the speaker was from dialect region 8 (nomadic), was male with speaker code \texttt{JLN0}, and spoke sentence code \texttt{SA1}, which reads ``She had your dark suit in greasy wash water all year''.
-After downsampling, the signal was compressively sampled with a \replaced{CR}{compression ratio} of 40\% using 1024 frames and 75\% frame overlap.
+After downsampling, the signal was compressively sampled with a CR of 40\% using 1024 frames and 75\% frame overlap.
 The optimal regularization $\alpha$ was determined automatically via 5-fold cross validation, and the reconstruction result is shown in Fig.~\ref{fig:recovered}.
@@
 
-Next, the error maps for the signal were generated by compressively sensing the signal and evaluating the metrics for varying \replaced{CR}{compression ratios} $m/n \in [0.1, 0.9]$ (in increments of 0.1) and number of frames/subbands $\in \qty{128, 256, 512, 1024}$, while keeping the frame overlap constant.
+Next, the error maps for the signal were generated by compressively sensing the signal and evaluating the metrics for varying CR $m/n \in [0.1, 0.9]$ (in increments of 0.1) and number of frames/subbands $\in \qty{128, 256, 512, 1024}$, while keeping the frame overlap constant.
 Figure \ref{fig:pesq-snr} shows the PESQ map (left) and the \snrseg~map (right).
-The former exhibits sensitivity to the \replaced{CR}{compression ratio} and achieves a value of 4.0 (good) at around 70\% compression.
-The latter tells a different story: it shows sensitivity towards the number of frames/subbands (as it is an \textit{average} metric) with some additional degradation at lower \replaced{CR}{compression ratios}, and achieves a maximum value of 0.08 at around 1024 frames.
+The former exhibits sensitivity to the CR and achieves a value of 4.0 (good) at around 70\% compression.
+The latter tells a different story: it shows sensitivity towards the number of frames/subbands (as it is an \textit{average} metric) with some additional degradation at lower CR, and achieves a maximum value of 0.08 at around 1024 frames.
 
@@
 \section{Conclusions}
-The reconstruction quality of compressively sampled audio signals containing speech recordings was \linelabel{ln:pesq-conc}\replaced{described by varying}{shown to be dependent on} two distinct factors\added{, namely, the compression ratio and number of subbands/sampling windows.}\deleted{as well as the metric being used.} Evaluation of a perceptually intuitive metric such as PESQ shows that it is sensitive to changes in compression \added{but independent of the number of spectrogram subbands}, wherein a compression ratio of 60\% is sufficient to yield an average (3.0) PESQ score.
-On the other hand, evaluation of a statistically-based metric such as \snrseg~shows that it is sensitive to changes in the number of \replaced{subbands}{frames} used to represent the signal in the spectrogram domain, where the use of more frames yields a higher \snrseg~score.
+The reconstruction quality of compressively sampled audio signals containing speech recordings was described by varying two distinct factors, namely, the compression ratio and number of subbands/sampling windows.
+Evaluation of a perceptually intuitive metric such as PESQ shows that it is sensitive to changes in compression but independent of the number of spectrogram subbands, wherein a compression ratio of 60\% is sufficient to yield an average (3.0) PESQ score.
+On the other hand, evaluation of a statistically-based metric such as \snrseg~shows that it is sensitive to changes in the number of subbands used to represent the signal in the spectrogram domain, where the use of more frames yields a higher \snrseg~score.
 

### 2020-07-03 Response to Reviewer Comments.tex
1st reviewer revisions

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\parindent=0pt
\parskip=10pt

\begin{document}

\section*{Response to Reviewer Comments}

Dear Reviewer,

Thank you for reviewing our paper entitled ``Compressively sampled speech: How good is the recovery?'' and helping us improve our work. The following is our response to the points raised in your review. The texts in green show the changes we made in the paper.

\begin{enumerate}
	\item
		\begin{enumerate}
			\item \textbf{You are able to clearly present why using PESQ is advantageous over other metrics. However, in the introduction, I think discussion on how the algorithm works, how it is determined, etc. is lacking. Upon reading your paper, I just treated it as a blackbox algorithm. Adding a couple of sentences could prove helpful to the reader.}

			The algorithm of PESQ is quite long and complex, and we could not summarize it in the paper---even in diagram form---without going over the page limit. We refer the reader to the source material instead in Sec.~2.4, Paragraph 1:

			\begin{quotation}
				\textcolor{Green}{Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual [8] for an in-depth discussion.}
			\end{quotation}
		\end{enumerate}

	\item
		\begin{enumerate}
			\item \textbf{Optional change: If possible, I would prefer it if you move the figures near where you mention them instead of all at the end.}

			From what we know, LaTeX automatically optimizes the positioning of elements in order to maximize space (and minimize page count). Thus, we opted to leave the positioning of the figures to the compiler.
		\end{enumerate}

	\item
		\begin{enumerate}
			\item \textbf{For future studies, can you try multiple audio files/samples? Maybe the results are specific for the audio sample (or explain why it is a good representative aside from being a random sample). However, I think the most important idea in this paper is using PESQ as a metric for CS-reconstructed audio signals so I think it can stand on its own without requiring more samples.}

			We conducted experiments on various audio files which also came from the TIMIT dataset and the results were consistent following the same procedure. This is most likely due to the consistency of the dataset as well, i.e., a number of unique sentences spoken by people with different accents and genders, all cleanly recorded at a rate of 16 kHz. The specific audio file used in this paper is simply a representative case based on all the previous experiments. For future studies, we can test signals from other datasets or record our own. You are correct regarding the important idea of the paper.

			\item \textbf{Change ``At face value'' to ``Visually,''. Remove ``we can immediately tell''.}

			By ``At face value'', we are referring to the value of PESQ. To avoid confusion, we have replaced the sentence to the following:

			\begin{quotation}
				\textcolor{Green}{By inspection of the PESQ value alone, we can tell that the reconstructed signal quality is slightly below average.}
			\end{quotation}

			\item \textbf{How do you determine ``slightly below average''?}

			The PESQ algorithm was modeled on subjective scoring systems. Such systems would ask people to rate an output signal, say, an integer from 1 to 5, given the input signal. In that case, 1 would correspond to bad, and 5 excellent. The output of PESQ is a float, but the authors still have opted to label the integer scores as 1.0 - bad, 2.0 - below average, 3.0 - average, 4.0 - good, 5.0 - perfect. The test signal yielded a PESQ value of 2.50, which is slightly below average.
		\end{enumerate}
\end{enumerate}

\end{document}

### 2020-07-03 List of Changes.tex
1st reviewer revisions

\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\parindent=0pt
\parskip=10pt

\begin{document}

\section*{List of Changes}

\begin{itemize}
	\item \textbf{Abstract}: Incorporated changes suggested by the reviewer.
		\begin{itemize}
			\item Last sentence: removed ``It is shown''
		\end{itemize}

	\item \textbf{Introduction}: Incorporated changes suggested by the reviewer.
		\begin{itemize}
			\item Paragraph 1: removed Eq.~(1) and replaced preceding sentence with ``...sampled at a rate at least twice the signal's highest frequency component.''
			\item Paragraph 2: replaced ``impossible'' with ``infeasible''
		\end{itemize}
	\item \textbf{Methodology}: Incorporated changes suggested by the reviewer.
		\begin{itemize}
			\item Sec.~2.2: replaced ``some domain'' with ``a domain''
		\end{itemize}
	\item \textbf{Results \& Discussion}: Incorporated changes suggested by the reviewer.
		\begin{itemize}
			\item Paragraph 1: replaced ``appears to have decreased'' with ``decreased''
			\item Last sentence: removed ``However''
		\end{itemize}
\end{itemize}

\end{document}

### 2020-07-03 main.tex
1st reviewer revisions

@@
 Modern signal acquisition technologies are made possible by the Nyquist-Shannon sampling theorem (NST).
-However, this paradigm is extremely wasteful as the signal is compressed before storing it by systematically discarding the imperceptible information.
+However, this paradigm is extremely wasteful as the signal is compressed before storing it by systematically discarding imperceptible information.
 Compressive sensing (CS) aims to directly sense the relevant information.
@@
 In this paper, we quantify the reconstruction quality of compressively sampled speech with a perceptually intuitive metric---the Perceptual Evaluation of Speech Quality (PESQ)---and with the standard average segmental SNR (\snrseg).
-It is shown that the quality of recovery of compressively sampled speech evaluated using PESQ is dependent on the compression ratio, and independent of the number of subbands used to represent the signal in the spectrogram domain.
+The quality of recovery of compressively sampled speech evaluated using PESQ is dependent on the compression ratio, and independent of the number of subbands used to represent the signal in the spectrogram domain.
 
@@
 \section{Introduction}\label{sec:intro}
-Conventional sensing devices are based on the Nyquist-Shannon sampling theorem (NST), which states that given a signal's bandwidth, one can capture all the pertinent information about that signal if it is sampled at a rate
-
-\begin{equation} \label{eq:nst}
-	f_S \geq 2f_B
-\end{equation}
-
-\noindent where $f_B$ is the signal's highest frequency component, and $2f_B$ is known as the Nyquist rate.
-After this sampling process, the information is compressed by exploiting the signal's natural compressibility in some transform domain.
-For standard daily tasks, this tried-and-true method of sampling and systematically discarding the imperceptible information is acceptable for most applications.
-However, in certain situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful.
+Conventional sensing devices are based on the Nyquist-Shannon sampling theorem (NST), which states that given a signal's bandwidth, one can capture all the pertinent information about that signal if it is sampled at a rate at least twice the signal's highest frequency component.
+After sampling, information is compressed by exploiting the signal's natural compressibility in some transform domain.
+For most applications, this tried-and-true method of sampling and systematically discarding the imperceptible information is acceptable.
+However, in situations when transmission bandwidth and/or storage comes at a premium, this process is highly wasteful.
 Cand\'{e}s et al.
@@
 
-In other words, the signal vector $\vec{x} \in \mathbb{R}^n$ is correlated with the basis waveforms $\vec{a}_k$ to yield a compressed information vector $\vec{y} \in \mathbb{R}^m$, where $m \ll n$.
-This causes the task of recovering $\vec{x}$ from $\vec{y}$ impossible since there exist an infinite number of candidate solutions $\bm\hat{\vec{x}}$ which satisfy \eqref{eq:cesa}.
+The signal vector $\vec{x} \in \mathbb{R}^n$ is correlated with the basis waveforms $\vec{a}_k$ to yield a compressed information vector $\vec{y} \in \mathbb{R}^m$, where $m \ll n$.
+This causes the task of recovering $\vec{x}$ from $\vec{y}$ infeasible since there exist an infinite number of candidate solutions $\bm\hat{\vec{x}}$ which satisfy \eqref{eq:cesa}.
 This can be circumvented by enforcing sparsity and incoherence constraints \cite{Candes2008b} based on models of natural signals.
@@
 \subsection{Transforming to a sparse domain}\label{ssec:sparse}
-The first requirement for CS is that a signal should be transformed to some domain where it can be represented sparsely.
+The first requirement for CS is that a signal should be transformed to a domain where it can be represented sparsely.
 In the case of recorded speech, the most appropriate domain would be the modulation domain, otherwise known as its spectrogram.
@@
 \subsection{Reconstruction evaluation}\label{ssec:eval}
-Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS). The \snrseg~, defined as
+Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).
+Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual \cite{pesq} for an in-depth discussion.
+
+The \snrseg~, defined as
 
@@
 The optimal regularization $\alpha$ was determined automatically via 5-fold cross validation, and the reconstruction result is shown in Fig.~\ref{fig:recovered}.
-Qualitative comparison in the temporal domain shows that the waveforms of the original and reconstructed are similar; in the modulation domain, the dynamic range appears to have decreased, but the dominant frequencies can still be observed.
+Qualitative comparison in the temporal domain shows that the waveforms of the original and reconstructed are similar; in the modulation domain, the dynamic range decreased, but the dominant frequencies can still be observed.
 Evaluating the PESQ and \snrseg~yields values of 2.50 and 0.07, respectively.
-At face value, we can immediately tell from the PESQ that the reconstructed signal quality is slightly below average.
-However, this distinction cannot be made for the \snrseg~since its bounds are not clearly defined.
+By inspection of the PESQ value alone, we can tell that the reconstructed signal quality is slightly below average.
+This distinction cannot be made for the \snrseg~since its bounds are not clearly defined.
 

### 2020-08-16 Response to Reviewer Comments.tex
2nd reviewer revisions

@@
 	\end{enumerate}
+
+	\item
+		\begin{enumerate}
+			\item \textbf{Please incorporate changes that you mentioned in your reply to the reviewer but was not added to the manuscript.
+For example, add the conversion table from number to qualitative description -- "slightly below average".}
+
+			We have added Table 1 in Sec.~2.4 for the conversion of PESQ from quantitative to qualitative. In the preceding paragraph, the following sentence has been added:
+
+			\begin{quotation}
+				...models the obsolete mean opinion scores (MOS). \textcolor{Green}{Its output is a float in the range $[1, 5]$ with corresponding qualitative descriptions at integer values, as shown in Table~1.}
+			\end{quotation}
+		\end{enumerate}
 \end{enumerate}

### 2020-08-16 main.tex
2nd reviewer revisions

@@
 \usepackage{amsfonts}
-\usepackage{changes}
+\usepackage{tabularx}
 \usepackage{graphicx}
@@
 Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).
+Its output is a float in the range $[1, 5]$ with corresponding qualitative descriptions at integer values, as shown in Table~\ref{tab:pesq}.
 Due to the complexity of the algorithm, we refer the reader to Sec.~10 of the PESQ manual \cite{pesq} for an in-depth discussion.
 
-The \snrseg~, defined as
+\begin{table}[htb]
+	\centering
+	\caption{PESQ integer values and their corresponding qualitative descriptions.}
+	\label{tab:pesq}
+	\begin{tabularx}{\textwidth}{ >{\bfseries}r *{5}{| >{\centering\arraybackslash}X} }
+		PESQ value & 1 & 2 & 3 & 4 & 5 \\
+		Description & bad & below average & average & good & perfect
+	\end{tabularx}
+\end{table}
+
+The \snrseg, defined as
 

### 2020-10-19 Response to Reviewer Comments.tex
1st draft slides

@@
 \parskip=10pt
+
+\newcommand{\pagelineref}[1]{Page~\pageref{#1}, Line~\lineref{#1}}
 
@@
 
+\section*{List of Changes}
+
+\begin{itemize}
+	\item \textbf{Abstract}: Incorporated changes suggested by the reviewer.
+	\begin{itemize}
+		\item Last sentence: removed ``It is shown''
+	\end{itemize}
+
+	\item \textbf{Introduction}: Incorporated changes suggested by the reviewer.
+	\begin{itemize}
+		\item Paragraph 1: removed Eq.~(1) and replaced preceding sentence with ``...sampled at a rate at least twice the signal's highest frequency component.''
+		\item Paragraph 2: replaced ``impossible'' with ``infeasible''
+	\end{itemize}
+	\item \textbf{Methodology}: Incorporated changes suggested by the reviewer.
+	\begin{itemize}
+		\item Sec.~2.2: replaced ``some domain'' with ``a domain''
+		\item Sec.~2.4: added ``...which models the obsolete mean opinion scores (MOS) \textcolor{Green}{obtained from human observers}.''
+	\end{itemize}
+	\item \textbf{Results \& Discussion}: Incorporated changes suggested by the reviewer.
+	\begin{itemize}
+		\item Paragraph 1: replaced ``appears to have decreased'' with ``decreased''
+		\item Last sentence: removed ``However''
+	\end{itemize}
+\end{itemize}
+
 \end{document}

### 2020-10-19 main.tex
1st draft slides

@@
 \subsection{Reconstruction evaluation}\label{ssec:eval}
-Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS).
+Reconstruction quality was evaluated using PESQ, which is a full-reference, perceptually intuitive scoring system which models the obsolete mean opinion scores (MOS) obtained from human observers.
 Its output is a float in the range $[1, 5]$ with corresponding qualitative descriptions at integer values, as shown in Table~\ref{tab:pesq}.
@@
 	\centering
-	\subfloat[Original]{\makebox[0.46\textwidth]{{\includegraphics[width=0.46\textwidth]{original.png}\label{fig:original}}}}
+	\subfloat[Original]{\makebox[0.46\textwidth]{{\includegraphics[width=0.45\textwidth]{original.png}\label{fig:original}}}}
 	\quad % or other spacing between figures
-	\subfloat[Recovered]{\makebox[0.46\textwidth]{\includegraphics[width=0.46\textwidth]{recovered.png}\label{fig:recovered}}}
+	\subfloat[Recovered]{\makebox[0.46\textwidth]{\includegraphics[width=0.45\textwidth]{recovered.png}\label{fig:recovered}}}
 	\caption{Test speech signal obtained from the TIMIT speech corpus with the (a) original signal, and (b) reconstructed signal from compressive measurements.
@@
 	\centering
-	\includegraphics[width=\textwidth]{metrics.png}
+	\includegraphics[width=0.89\textwidth]{metrics.png}
 	\caption{Two most commonly used metrics in evaluating quality of reconstructed speech recordings.
